Understanding Bicycle Theft in High-Risk Neighborhoods: Key Predictors for Targeted Risk Assessment

### 2024-12-03 paper/paper.qmd
Final Edits

This research provides actionable knowledge to enhance theft prevention in urban settings. By identifying the circumstances under which thefts are more likely to occur, the study offers evidence to inform targeted interventions, such as improved security measures in vulnerable areas. These findings contribute to creating safer urban spaces for cyclists.

@@

@@

>>>>

Bicycle theft is a persistent issue in urban environments, imposing economic and emotional burdens on individuals and communities. As cities like Toronto increasingly embrace cycling as a sustainable transportation mode, mitigating theft is essential for maintaining public trust in cycling infrastructure. However, existing studies often focus on general crime trends, overlooking the nuanced factors that drive bicycle theft in specific high-risk neighborhoods.

This study addresses this gap by analyzing reported bicycle thefts in Toronto. Using statistical modeling, it identifies contextual factors such as premises type, time of occurrence, and bike cost that influence theft likelihood in high-risk neighborhoods. By focusing on these areas, the research highlights actionable risk factors and proposes strategies to prevent theft and enhance cyclist security.

@@

The results of the Bayesian logistic regression model emphasize the role of contextual and temporal factors in shaping bicycle theft patterns. Key findings include:

- Premises Type: Theft risk is significantly higher in public spaces such as streets and parks compared to residential premises, likely due to lower security measures.
- Time of Day: The likelihood of theft increases during evening hours, reflecting reduced visibility and activity.
- Bike Cost: High-cost bicycles are more frequently targeted, underscoring their appeal to thieves.

@@

## Implications for Urban Policy
These findings suggest actionable strategies for reducing bicycle theft in urban areas by addressing vulnerabilities in public spaces. High-risk locations, such as streets, parks, and transit areas, often lack adequate security measures, making them prime targets for theft. Implementing targeted interventions, such as enhanced lighting, can deter criminal activity by increasing visibility and discouraging opportunistic behavior. Community policing, involving regular patrols and partnerships with local cycling groups, can create a sense of security and deter theft through increased accountability. Secure parking zones equipped with features such as CCTV surveillance, well-lit areas, and designated bike racks can provide cyclists
